Highly Available Transactions: Virtues and Limitations

### 2013-04-01 writeup/evaluation.tex
bah

Delivery is challenging due to non-monotonicity. Each Delivery deletes
a pending order from the NewOrder Table and should be idempotent in
order to avoid billing a customer twice; this implies a need to
prevent Lost Update. This issue  can be avoided  by moving the
non-monotonicity to the real world---the carrier that picks up the
package for an order can ensure that she is the only carrier who has
done so---but cannot provide a correct execution with HATs
alone. However, according to distributed transaction
architects~\cite{entitygroup}, these compensatory actions are
relatively common in real-world business processes.

>>>>

Delivery is challenging due to non-monotonicity. Each Delivery deletes
a pending order from the New-Order Table and should be idempotent in
order to avoid billing a customer twice; this implies a need to
prevent Lost Update. This issue  can be avoided  by moving the
non-monotonicity to the real world---the carrier that picks up the
package for an order can ensure that she is the only carrier who has
done so---but cannot provide a correct execution with HATs
alone. However, according to distributed transaction
architects~\cite{entitygroup}, these compensatory actions are
relatively common in real-world business processes.
